Parsing Postfix log files

### 2007-11-15 doc/logparser-acronyms.tex
Capitalised Wikipedia so it wouldn't be highlighted as a spelling error any more.  Silly?  Possibly.

\newacronym{SQL}{Structured Query Language}{description={
    SQL is the standard language used for database querying, modification
    and maintenance.  Some information about SQL, including its history,
    can be found at \cite{wikipedia-sql}.
}}

\newacronym{SPF}{Sender Policy Framework}{description={
    SPF is explained fully in~\cite{openspf, wikipedia-spf}.
}}

@@

\newacronym{regex}{Regular Expression}{description={
    Regular expressions are a method of matching patterns in text that are
    explained in detail in~\cite{wikipedia-regex, perlre} .
}}

@@

\newacronym{HTML}{Hypertext Markup Language}{description={
    HTML is the markup language designed for writing web
    pages~\cite{wikipedia-html, w3schools-html}.
}}

\newacronym{IP}{Internet Protocol address}{description={
    The Internet Protocol~\cite{wikipedia-ip} is the protocol used to
    communicate between computers on the Internet.  An IP address is a
    unique address assigned to a computer on the Internet, allowing it to
    communicate with other computers on the Internet.  For more information
    see~\cite{wikipedia-ip-address}.
}}

>>>>

\newacronym{SQL}{Structured Query Language}{description={
    SQL is the standard language used for database querying, modification
    and maintenance.  Some information about SQL, including its history,
    can be found at \cite{Wikipedia-sql}.
}}

\newacronym{SPF}{Sender Policy Framework}{description={
    SPF is explained fully in~\cite{openspf, Wikipedia-spf}.
}}

@@

\newacronym{regex}{Regular Expression}{description={
    Regular expressions are a method of matching patterns in text that are
    explained in detail in~\cite{Wikipedia-regex, perlre} .
}}

@@

\newacronym{HTML}{Hypertext Markup Language}{description={
    HTML is the markup language designed for writing web
    pages~\cite{Wikipedia-html, w3schools-html}.
}}

\newacronym{IP}{Internet Protocol address}{description={
    The Internet Protocol~\cite{Wikipedia-ip} is the protocol used to
    communicate between computers on the Internet.  An IP address is a
    unique address assigned to a computer on the Internet, allowing it to
    communicate with other computers on the Internet.  For more information
    see~\cite{Wikipedia-ip-address}.
}}

### 2007-11-15 doc/logparser.tex
Capitalised Wikipedia so it wouldn't be highlighted as a spelling error any more.  Silly?  Possibly.

    \item Checking \SPF{} records~\cite{openspf, wikipedia-spf}.  \SPF{}
        records specify which mail servers are allowed to send mail
        claiming to be from a particular domain.  The intention is to
        reduce spam from faked sender addresses,
        backscatter~\cite{postfix-backscatter} and joe
        jobs~\cite{wikipedia-joe-job}; however there has been a lot of
        resistance to the proposal because it breaks or vastly complicates
        some features of \SMTP{}\@.

@@

The parser does not try to detect overlapping rules;\footnote{It may be
possible to parse each rule's \regex{}, generate a \DFA{} from it, and
examine every \DFA{} to determine if any overlap.  The author has not
attempted to do this: such a project by itself would probably qualify for a
PhD, and may involve solving the Halting
Problem~\cite{wikipedia-halting-problem} and circumventing the
Church-Turing Thesis~\cite{wikipedia-church-turing-thesis}.} that
responsibility is left to the author of the rules.  Unintentionally
overlapping rules lead to inconsistent parsing and data extraction because
the order in which rules are tried against each line is unspecified, and
the first matching rule wins.  Overlapping rules are frequently a
requirement, allowing a more specific rule to match some lines and a more
general rule to match the majority, e.g.\ separating \SMTP{} delivery to a
specific sites from \SMTP{} delivery to the rest of the world.  The
algorithm provides a facility for ordering overlapping rules: the priority
field in each rule (defaults to zero).  Rules are sorted by priority,
highest first, and then rules with the same priority are sorted by the
number of successful matches when parsing the previous log file.  Negative
priorities may be useful for catchall rules.

@@

\glossary{name={Phishing},description={
    Phishing~\cite{wikipedia-phishing} is an attempt to acquire information
    by masquerading as an entity trusted by the user, e.g.\ a bank.
}}

@@

\glossary{name={IPv4},description={
    Internet Protocol~\cite{wikipedia-ipv4} version 4 is the fourth version
    of the Internet Protocol used to interconnect computers on the
    Internet.  It is the first widely deployed version of IP, and has been
    in use for over 25 years.
}}

\glossary{name={IPv6},description={
    Internet Protocol~\cite{wikipedia-ipv6} version 6 is the latest version
    of the Internet Protocol used to interconnect computers on the
    Internet.  It is the successor to IPv4, bringing with it a greatly
    expanded address space, allowing many more computers to use the
    Internet simultaneously.  IPv4 and IPv6 will coexist for many years to
    come as existing networks transition from the former to the latter.
}}

>>>>

    \item Checking \SPF{} records~\cite{openspf, Wikipedia-spf}.  \SPF{}
        records specify which mail servers are allowed to send mail
        claiming to be from a particular domain.  The intention is to
        reduce spam from faked sender addresses,
        backscatter~\cite{postfix-backscatter} and joe
        jobs~\cite{Wikipedia-joe-job}; however there has been a lot of
        resistance to the proposal because it breaks or vastly complicates
        some features of \SMTP{}\@.

@@

The parser does not try to detect overlapping rules;\footnote{It may be
possible to parse each rule's \regex{}, generate a \DFA{} from it, and
examine every \DFA{} to determine if any overlap.  The author has not
attempted to do this: such a project by itself would probably qualify for a
PhD, and may involve solving the Halting
Problem~\cite{Wikipedia-halting-problem} and circumventing the
Church-Turing Thesis~\cite{Wikipedia-church-turing-thesis}.} that
responsibility is left to the author of the rules.  Unintentionally
overlapping rules lead to inconsistent parsing and data extraction because
the order in which rules are tried against each line is unspecified, and
the first matching rule wins.  Overlapping rules are frequently a
requirement, allowing a more specific rule to match some lines and a more
general rule to match the majority, e.g.\ separating \SMTP{} delivery to a
specific sites from \SMTP{} delivery to the rest of the world.  The
algorithm provides a facility for ordering overlapping rules: the priority
field in each rule (defaults to zero).  Rules are sorted by priority,
highest first, and then rules with the same priority are sorted by the
number of successful matches when parsing the previous log file.  Negative
priorities may be useful for catchall rules.

@@

\glossary{name={Phishing},description={
    Phishing~\cite{Wikipedia-phishing} is an attempt to acquire information
    by masquerading as an entity trusted by the user, e.g.\ a bank.
}}

@@

\glossary{name={IPv4},description={
    Internet Protocol~\cite{Wikipedia-ipv4} version 4 is the fourth version
    of the Internet Protocol used to interconnect computers on the
    Internet.  It is the first widely deployed version of IP, and has been
    in use for over 25 years.
}}

\glossary{name={IPv6},description={
    Internet Protocol~\cite{Wikipedia-ipv6} version 6 is the latest version
    of the Internet Protocol used to interconnect computers on the
    Internet.  It is the successor to IPv4, bringing with it a greatly
    expanded address space, allowing many more computers to use the
    Internet simultaneously.  IPv4 and IPv6 will coexist for many years to
    come as existing networks transition from the former to the latter.
}}
